% resume.tex
%
%  J. Borzilleri <jonathan.borzilleri@gmail.com> http://www.asylumsw.com
%
%  Based off tex resume:
%  (c) 2002 Matthew M. Boedicker <mboedick@mboedick.org> http://mboedick.org
%
\documentclass[11pt]{article}
\usepackage{fullpage}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\usepackage{helvetica}
\usepackage{hyperref}
\hypersetup{
	colorlinks,
	urlcolor=cyan
}

\begin{document}

\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
\LARGE \textbf{Jonathan Marc Borzilleri}  & \\
800 Queen Anne Ave. North, Apt 502 &
	585-214-9359 \\
Seattle, WA 98109-4086 &
	\href{mailto:jonathan.borzilleri.jobs@gmail.com}{jonathan.borzilleri.jobs@gmail.com} \\
\href{http://github.com/duaiwe}{On GitHub} &
	\href{http://twitter.com/duaiwe}{@duaiwe} \\
\end{tabular*}

\hrule

\vspace{0.25in}
{\Large \textbf{Skills}}
\begin{description}
\item[Languages:] \hfill \\
Proficient in: PHP, Perl, HTML, CSS, Javascript, SQL, Bash, Java. \\
Experience with: Ruby, Python, VB.NET, C/C++, \LaTeX

\item[Technologies \& Tools:] SQL (MySQL, SQL Server), MongoDB, Backbone, jQuery,
SASS, Amazon EC2.

\item[Software:] Experience developing on all major operating systems,
though Linux \& Vim is my preferred environment. I have experience with
Git, SVN, Hg, Jenkins, and Ant.
\end{description}

\vspace{0.2in}
{\Large \textbf{Experience}}
\begin{itemize}

\item
	\begin{tabular*}{6in}[t]{l@{\extracolsep{\fill}}r}
		\textbf{Intrepid Learning} & March 2010 - Present \\
		\textbf{Applications Developer} & Seattle, WA \\
	\end{tabular*}

	Intrepid Learning focuses on corporate training and learning services,
	covering a range from sourcing of training instructors to client sites to
	providing custom designed hosted informal learning portals. Its clients include
	Boeing and State Stree Global Advisors.

	At Intrepid, I lead the development of a web framework designed specifically
	to integrate with our internal CMS via a REST based API, several client sites
	have been implemented and released based on this framework. Much of my work
	has been keeping this framework up to date with changes to the API, requiring
	working closely with that development team and having significant knowledge
	of its codebase. I have also stepped into the role of release manager for
	our client apps, developing tools to smooth our release process, and
	managing branches in our git repository to ensure the correct code is released.

	\begin{itemize}
		\item Lead developer of PHP web framework designed to interact with REST
		API back end.
		\item Implemeted a REST API in this framework for third party integrations
		\item Developed web apps on top of this framework using modern Javascript
		and CSS techniques.
		\item Managed builds and releases of apps, developed tools to ease deployments.
	\end{itemize}

\item
	\begin{tabular*}{6in}[t]{l@{\extracolsep{\fill}}r}
		\textbf{Tweetajob} & September 2009 - December 2009 \\
		\textbf{PHP/MySQL Web Development} & Seattle, WA \\
		\end{tabular*}

		Tweetajob was a small startup focused on leveraging Twitter
		as a platform for job postings, allowing job seekers to subscribe to field
		and location focused twitter feeds. It attempted to monetize itself by
		allowing recruiters to easily and cheaply post positions to a matrix of
		locations and fields.

		I was primarily responsible for developing the admin console, which allowed
		for managing recruiter users, monitoring tweets made by the system,
		and performing other site management. Additionally, I implemented part of
		the payment processing system, using Authorize.NETs API to handle
		one-off and recurring payments.

		\begin{itemize}
			\item Used Twitter's API to implement functionality to monitor and
			delete tweets made by the system.
			\item Used Authorize.NET API to implement one-off and recurring
			payment processing.
			\item Developed admin console for managing users, payments, and
			tweet interaction.
		\end{itemize}

\item
	\begin{tabular*}{6in}[t]{l@{\extracolsep{\fill}}r}
		\textbf{Implied Solutions, LLC} & March 2009 - May 2009 \\
		\textbf{PHP/MySQL Web Development} & Seattle, WA \\
		\end{tabular*}

		Implied Solutions is a small consulting company, focused on
		developing and designing client sites. I was the primary developer behind
		the \textit{Running Rewards} site, which was designed to engage the
		marathon/ running community and provide information on event goodie bags
		and other incentives.

		I built the site using PHP, using the Doctrine ORM to interact with the
		MySQL database. I took photoshop files from a designer and used them to
		build the site's interface.

		\begin{itemize}
			\item Primary developer behind \textit{Running Rewards} web site.
			\item Developed using OO PHP, Doctrine ORM, \& MySQL
			\item Designed \& developed site based on client requirements.
			\item Implemented UI based on designer photoshop mockups.
		\end{itemize}

\item
	\begin{tabular*}{6in}[t]{l@{\extracolsep{\fill}}r}
		\textbf{The Active Network} & June 2007 - September 2008 \\
		\textbf{Thriva - SOA Development} & Bothell, WA \\
		\end{tabular*}

		The Active Network focuses on online registration and event management
		software, and acquired Thriva in 2007. Thriva built a hosted web-based
		event management solution, which included online registration, database
		management, and payment processing.

		I was the lead developer for the "SOA" project, which was the SOAP
		interface and business logic application for Thriva. In addition to
		maintenance and feature improvements of this application, I also developed
		two Windows Service applications. One I designed and built for processing
		recurring payments based on customer and/or user defined schedules and
		amounts.

		Another was designed to split up the user registration process into an
		asynchronous service, to improve performance. By performing the minimum of
		data and payment validation in line with the user registration and
		offloading the heavy lifting of registration persistance, I significantly
		improved the performance of the registration process.

		\begin{itemize}
			\item Lead developer for SOA project, the SOAP interface and business
			logic application for Thriva product.
			\item Worked heavily in SQL Server, developing stored procedures \& views.
			\item Lead development for a windows service app to handle asyncronous
			processing of data across multiple sql server databases.
		\end{itemize}

\end{itemize}

\vspace{0.2in}
{\Large \textbf{Interests/Hobbies}}
\begin{itemize}
\item
	\begin{tabular*}{6in}[t]{l@{\extracolsep{\fill}}r}
		\textbf{Norwescon} & 2011 - 2012 \\
		\textbf{IT Developer} & \\
	\end{tabular*}

	Last year I started volunteering for Norwescon, a local science fiction/fantasy
	literature convention. I performed a variety of IT \& developer roles, including
	maintenence on existing software \& web apps, setup/teardown of the at-con
	network infrastructure, and at-con tech support for the registration and art
	show systems.

\item
	\begin{tabular*}{6in}[t]{l@{\extracolsep{\fill}}r}
		\textbf{Game Development} & \\
	\end{tabular*}

	\begin{itemize}
		\item I currently run and administer servers for Minecraft and Terraria for
		myself and friends. For Minecraft, I have implemented automatic map
		generation using an open source mapping tool, automated backup snapshots
		using rsyncbackup, and off-machine backups (though, not offsite,
		as both machines are VPS's in the same datacenter).

		\item I have developed Mods for both Minecraft and World of Warcraft.
		Minecraft mods were developed in Java using the community developed Bukkit
		API \& Server implementation. The WoW addons were developed in lua.
		Source code for these mods can be found in my github profile:
		\href{http://github.com/duaiwe}{http://github.com/duaiwe}
	\end{itemize}

\item
	\begin{tabular*}{6in}[t]{l@{\extracolsep{\fill}}r}
		\textbf{Hiking \& Snowboarding} & \\
	\end{tabular*}

	Though I am not able to go as much as I would like, I enjoy hiking, and have
	enjoyed hiking various areas of the pacific northwest, and snowboarding at
	crystal mountain.

\end{itemize}



\vspace{0.2in}
{\Large \textbf{Education}}
\begin{itemize}
\item
	\begin{tabular*}{6in}[t]{l@{\extracolsep{\fill}}r}
		\textbf{Rochester Institute of Technology} & Rochester, NY \\
		Bachelor of Science in Computer Science & \\
		Minor in Philosophy & \\
	\end{tabular*}
\end{itemize}

% \vspace{0.2in}
% \textbf{References available upon request.}

\end{document}

